Introduction to *cellcount* - Draft vignette

### 2024-03-18 cellcount_intro.Rmd
Minor updates - changed data.frame column header

```{r,include=FALSE}
outlier_detect<-function(){
  mean<-median(Demo.Results$Cell_Count)
  sd<-sd(Demo.Results$Cell_Count)*2
  sd_neg<-(mean-sd)
  sd_pos<-(mean+sd)
  SD_range_detection<-ifelse(sd_pos>Demo.Results$Cell_Count,Demo.Results$Cell_Count,NA)&
    ifelse(sd_neg<Demo.Results$Cell_Count,Demo.Results$Cell_Count,NA)
  return(SD_range_detection)
}
```
```{r}
Demo.Results$Cell_Count<-as.numeric(Demo.Results$Cell_Count)
Demo.Results$SD_range<-outlier_detect()
Demo.Results
```

@@

Demo.Results$Cell_Count<-as.numeric(Demo.Results$Cell_Count)
Demo.Results$SD_range<-outlier_detect()

>>>>

```{r,include=FALSE}
outlier_detect<-function(){
  mean<-median(Demo.Results$Cell_Count)
  sd<-sd(Demo.Results$Cell_Count)*2
  sd_neg<-(mean-sd)
  sd_pos<-(mean+sd)
  SD_range_detection<-ifelse(sd_pos>Demo.Results$Cell_Count,Demo.Results$Cell_Count,NA)&
    ifelse(sd_neg<Demo.Results$Cell_Count,Demo.Results$Cell_Count,NA)
  return(SD_range_detection)
}
```
```{r}
Demo.Results$Cell_Count<-as.numeric(Demo.Results$Cell_Count)
Demo.Results$within_outlier_range<-outlier_detect()
Demo.Results
```

@@

Demo.Results$Cell_Count<-as.numeric(Demo.Results$Cell_Count)
Demo.Results$within_outlier_range<-outlier_detect()
